Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity

### 2016-06-14 completeness.tex
fixing figures
working on comppleteness figure

\begin{table*}[t]
    \centering
    \caption{Year thresholds and magnitude completeness for the seismic zones within the region of interest in this study.}
    \begin{tabular}{lccccrc}
    	\cline{2-7}                                              \\[-1.6ex]
                        & 3--4 & 4--5 & 5--6 & 6--7 & 
                                  \multicolumn{1}{c}{$>7$} &$M_c$\\[0.6ex]
        \hline                                                   \\[-1.6ex]
        Azerbaijan      & 1961 & 1961 & 1900 & 1581 & 1042 & 4.5 \\
        Alborz          & 2005 & 1950 & 1900 & 1664 &--401 & 4.4 \\
        Kopeh Dagh      & 2005 & 1950 & 1900 & 1673 &    9 & 4.5 \\
        Zagros          & 2005 & 1961 & 1900 & 1853 & 1439 & 4.4 \\
        Central-East    & 2005 & 1961 & 1854 & 1837 &  762 & 4.5 \\
        Uniform Model   & 2005 & 1961 & 1900 & 1778 &--401 & 4.5 \\[0.5ex]
        \hline 
    \end{tabular}
    \label{tab:params} 
\end{table*}

@@

An important property of a seismic catalog is its completeness, which is measured both in terms of the magnitude above w....

This parameter defines the minimum magnitude at which the seismic catalog of a region can be considered complete within a certain time period, and is used as input to the seismic analysis.

...which varies according to magnitude, is used as input during the seismic hazard analysis process. It basically consists in determining the point at which catalog data show a steady occurrence of events. There are multiple approaches to determine the completeness of a catalog. A simple approach used by \citet{Frankel1995} and others is to identify the year at which the rate of events becomes constant. In other words, if looking at a plot of cumulative number of events of a given magnitude range with respect to time, the catalog is assumed to be complete from the year at which moving forward the plot follows a straight line. A similar approach based on the maximum value of the first derivative of the frequency-magnitude curve is implemented in the ZMAP software \citep{Wiemer2001}.

One of the difficulties in determining completeness is the availability of data for a long-enough period of time for all magnitude ranges, especially for large magnitude earthquakes of low recurrence. \citet{Zare} provide the years for catalog completeness in their the original catalog for the different regions in their study on the seismicity of the Middle East. They used the

4.5, and 4.4 for 
Central Iran, and Zagros tectonic seismic regions, respectively. For the uniform model we used 4.5 as a completeness magnitude.

% 		& Azerbaijan  & Alborz & Kopeh Dagh & Central Iran & Zagros & North Iran  \\ \hline
% 3-4         & 1961  & 2005   & 2005       & 2005         & 2005   & 2005          \\ \hline
% 4-5         & 1961  & 1961   & 1950       & 1961         & 1961   & 1961          \\ \hline
% 5-6         & 1900  & 1900   & 1900       & 1854         & 1900   & 1900           \\ \hline
% 6-7         & 1581  & 1664   & 1673       & 1837         & 1853   & 1778           \\ \hline
% 7 $< $      & 1042  & -401   & 9          & 762          & 1439   & -401            \\

@@

According to \citet{Frankel1995}, we made plots of the cumulative number of events against time for different regions' catalog.

@@

>>>>

@@

An important aspect of seismic catalogs is their completeness.  Completeness is is measured both in terms of the year of completeness and the completeness magnitude. Both are used in the seismic analysis process. The year of completeness is the point in time at which catalog data exhibits a steady rate of event occurrence. This is measured for different magnitude ranges. A simple approach used by \citet{Frankel1995} and others is to identify the year at which a plot of the cumulative number of events with respect to time becomes (or at least, resembles) a straight line.

The completeness magnitude, on the other hand, is the minimum magnitude at which the seismic catalog of a region can be considered complete within a certain time period. While the year of completeness can be determined by inspection of the data, the completeness magnitude requires a numerical analysis of the catalog. A common approach is to identify the magnitude associated with the maximum value of the first derivative of the frequency-magnitude curve. This method is widely used as implemented in the ZMAP software package for seismic hazard analysis developed by \citet{Wiemer2001}.

One of the difficulties in determining completeness is the availability of data for a long-enough period of time for all magnitude ranges. In this study, we determined the year of completeness for magnitude ranges 3--4, 4--5, 5--6 and 6--7 by inspection, following the approach used by \citet{Frankel1995}. This is illustrated in Fig.~\ref{fig:completeness}, where we show the cumulative number of events with time for each of the seismic zones and magnitude ranges, and indicate our choice of completeness year thresholds. For events $M_w>7$, in which case there are no sufficient data to determine a proper threshold, we assumed the catalog to be complete from the earliest time at which there is record of large magnitude earthquakes.

The chosen years of completeness are compiled in Table \ref{tab:completeness}. Also shown in this table are the values of completeness magnitude for each seismic zone and for the uniform model of the entire region of interest.

... \citet{Zare} provide the years for catalog completeness in their the original catalog for the different regions in their study on the seismicity of the Middle East. They used the

@@

@@

\begin{figure*}[t]
    \centering
    \includegraphics[scale=0.28]{figures/pdf/figure-05.pdf} 
    \caption{Pending.}
    \label{fig:completeness}
\end{figure*}

\begin{table}[t]
    \centering
    \caption{Year thresholds and magnitude completeness for the seismic zones within the region of interest in this study.}
    \begin{tabular}{@{\hspace{0.2ex}}lccccrc@{\hspace{0.2ex}}}
        \cline{2-7}                                              \\[-1.6ex]
                        & 3--4 & 4--5 & 5--6 & 6--7 & 
                                  \multicolumn{1}{c}{$>7$} &$M_c$\\[0.6ex]
        \hline                                                   \\[-1.6ex]
        Azerbaijan      & 1961 & 1961 & 1900 & 1581 & 1042 & 4.5 \\
        Alborz          & 2005 & 1950 & 1900 & 1664 &--401 & 4.4 \\
        Kopeh Dagh      & 2005 & 1950 & 1900 & 1673 &    9 & 4.5 \\
        Zagros          & 2005 & 1961 & 1900 & 1853 & 1439 & 4.4 \\
        Central-East    & 2005 & 1961 & 1854 & 1837 &  762 & 4.5 \\
        Uniform Model   & 2005 & 1961 & 1900 & 1778 &--401 & 4.5 \\[0.5ex]
        \hline 
    \end{tabular}
    \label{tab:completeness} 
\end{table}
